\subsection{Android Game Programming}
As this is my first foray into game programming for Android the easiest solution would be to find a library that could handle the game engine functions, making it easier and quicker to develop as the game portion is not a integral part of the project.

\subsubsection{libgdx}
libGDX provides the perfect solution to my problem. It offers a cross-platform, open source solution to creating 2D and 3D games for Android, iOS, Windows/Mac/Linux desktop, web and others \cite{research:badlogix}. Alongside this Badlogic provides a simple tool for creating projects that can be imported into Eclipse which is detailed in the implementation section of this report.

There are numerous tutorials that detail the process of writing games for Android using libgdx, and a specific one that creates a Flappy Bird \cite{research:flappy_guardian} clone called Zombie Bird by Kilobolt \cite{research:kilo_tut}, from which a large proportion of knowledge was gained in terms of game and class design. They allow usage of assets free of charge to projects, and as such some of the images may be reused in Leaky Bird to speed up the development process.

\subsubsection{Game Design and Development}

It should be noted that this is peripheral to the main goal of this project. An application was required that would be believable in terms of users downloading it and not paying much attention to it, and be heavily used for a small period of time. As a result of this criteria an Android game was chosen to be developed; however, it does not focus heavily within the report. Detail is given to the funtionality required to leak the personal data, but not the internals of the game.